A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-08-26 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: Cite Grabish, Pap, Torra, Sugeno
Just a note to remember citing Grabish, Pap, Torra, and Sugeno on non-additive measure theory.

Lastly, we lay down the requirements for a non-additive generalization of probability theory, which should be in principle possible. Since there is a wide literature on the subject, [cite] we only show that the most used non-additive integrals, the Sugeno and Choquet integral, do not work for our purposes. This means that more work will be needed to develop the appropriate tools.

>>>>

Lastly, we lay down the requirements for a non-additive generalization of probability theory, which should be in principle possible. Since there is a wide literature on the subject, [cite Grabish, Pap, TorraSugeno] we only show that the most used non-additive integrals, the Sugeno and Choquet integral, do not work for our purposes. This means that more work will be needed to develop the appropriate tools.
